{\vspace{-2cm}}Temporal Congestion Analysis and Predictive Modeling of Ride-Hailing Trips in NYC Using High-Volume FHV Data

### 2025-04-22 paper.tex
chore: Draft paper.

\subsection{Data Acquisition and Setup}
I plan to obtain the NYC TLC High-Volume FHV trip record data set for all 12 months of 2024. Each monthly dataset is stored in Parquet format and can be accessed via Google Drive in a cloud-based Google Colab environment. I will use Apache Spark (PySpark) for all data ingestion and transformation steps, given the dataset's scale of over 200 million records.

@@

\section{Conclusion}
This proposed study is designed to demonstrate the value of using big data tools to analyze ride-hailing trip data to gain insight into congestion. It anticipates showing that simple predictive models can effectively estimate congestion levels using temporal features, while highlighting the importance of scalable infrastructure for large-scale mobility datasets. In future work, I may incorporate spatial features, extend modeling to multiyear data, or explore real-time streaming analysis.

>>>>

\subsection{Data Acquisition and Setup}
I plan to obtain the NYC TLC High-Volume FHV trip record data set for all 12 months of 2024 \cite{dataset}. Each monthly dataset is stored in Parquet format and can be accessed via Google Drive in a cloud-based Google Colab environment. I will use Apache Spark (PySpark) for all data ingestion and transformation steps, given the dataset's scale of over 200 million records.

@@

\section{Conclusion}
This proposed study is designed to demonstrate the value of using big data tools to analyze ride-hailing trip data to gain insight into congestion. It anticipates showing that simple predictive models can effectively estimate congestion levels using temporal features, while highlighting the importance of scalable infrastructure for large-scale datasets. In future work, I may incorporate spatial features, extend modeling to multiyear data, or explore real-time streaming analysis.
